Incidence of confirmed COVID-19 cases in care home staff and residents: Cohort study using electronic records in a large UK care home provider (March-June 2020)

### 2020-06-27 covidWarehouse/manuscript/manuscript.Rmd
improve life table calculations + add occupancy risk factor

---
title: "Incidence of confirmed COVID-19 cases in care home staff and residents: Cohort study using electronic records in a large UK care home provider (March-June 2020)"
# author: "Dutey-Magni, PF, Williams, H, Hayward, A, Shallcross, L"
date: "16/06/2020"
bibliography: references.bib
csl: elsevier-vancouver.csl
output:
  html_document:
    df_print: paged
    toc: yes
    code_folding: hide
  word_document:
    toc: yes
    reference_docx: template.docx
link-citations: yes
always_allow_html: yes
---

@@

date_min <- as.Date("2020-03-02")
date_max <- as.Date("2020-06-07") #as.Date("2020-06-15")
date_max_tallies = as.Date("2020-06-07")

@@

reference_homes <- reference_homes %>% 
  filter(home_code %in% home_inclusion) %>% 
  left_join(select(filter(beds, year=="2020"), -year)) %>% 
  mutate(staff_to_bed_ratio = staff_total/beds,
         carer_to_bed_ratio = (staff_care_assistants + staff_nurses)/beds,
         bed_tot_category = cut(.$beds, 
           breaks = seq(20,100,25), right = F, 
           paste0(seq(20, 80, 25), "–", seq(34, 94, 25), " beds")))

@@

residents_episodes <- tline %>% 
  filter(rday==1) %>% 
  group_by(resident_id, home_code, dob, gender, 
           status, home_type, user_type2,
           susceptible_symptomatic, 
           susceptible_confirmed) %>% 
  summarise(entry_date = min(date),
            exit_date = max(date+1),
            resident_days = sum(rday),
            susceptible_symptomatic_days = sum(susceptible_symptomatic),
            susceptible_confirmed_days = sum(susceptible_confirmed)) %>% 
  mutate(date1 = as.numeric( entry_date - date_min),
         date2 = as.numeric(exit_date - date_min),
         ageg = cut_age_denary(compute_age(dob, date_min), age.min = 75, age.max = 95)) %>% 
  mutate(symptomatic = -susceptible_symptomatic+1,
         confirmed = -susceptible_confirmed+1,
         symptomatic_confirmed = (-susceptible_symptomatic+1)*(-susceptible_confirmed+1),
         date2 = if_else(date1 == date2, date2 + 1, date2)) %>% 
  mutate(covid_status = case_when(
    symptomatic==0 & confirmed == 0 ~ "Negative",
    symptomatic==1 & confirmed == 0 ~ "Symptomatic (not confirmed)",
    symptomatic==0 & confirmed == 1 ~ "Asymptomatic confirmed",
    symptomatic==1 & confirmed == 1 ~ "Symptomatic confirmed"
  )) %>% 
  mutate(covid_status = factor(covid_status, 
                               levels = c("Negative", "Symptomatic (not confirmed)",
                                          "Asymptomatic confirmed", "Symptomatic confirmed")),
         ageg = cut_age_denary(compute_age(dob, date_min), age.min = 75, age.max = 95))   %>% 
  left_join(select(reference_homes, home_code, country, region_UK,
                   staff_to_bed_ratio, carer_to_bed_ratio, bed_tot_category)) %>% 
  group_by(resident_id) %>% 
  mutate(death_status = if_else(
    date1 == max(date1),
    as.integer(status == "Deceased"),
    0L
  )) %>% 
  ungroup()

residents_overview <- tline %>% 
  filter(rday==1) %>%
  mutate(ageg = cut_age_denary(compute_age(dob, date_min), age.min = 75, age.max = 95)) %>% 
  group_by(resident_id, home_code, ageg, gender, 
           admission_type2, home_type, user_type2, status) %>% 
  summarise(resident_days = sum(rday),
            susceptible_symptomatic_days = sum(susceptible_symptomatic),
            susceptible_confirmed_days = sum(susceptible_confirmed),
            symptomatic = max(-susceptible_symptomatic+1, na.rm = T),
            confirmed = max(-susceptible_confirmed+1, na.rm = T),
            start_date = min(date, na.rm = T),
            stop_date = max(date, na.rm = T),
            start_int = as.numeric(min(date, na.rm = T) - date_min),
            stop_int = as.numeric(max(date, na.rm = T)- date_min)
    ) %>% 
  ungroup() %>% 
  mutate(covid_status = case_when(
    symptomatic==0 & confirmed == 0 ~ "Negative",
    symptomatic==1 & confirmed == 0 ~ "Symptomatic (not confirmed)",
    symptomatic==0 & confirmed == 1 ~ "Asymptomatic confirmed",
    symptomatic==1 & confirmed == 1 ~ "Symptomatic confirmed"
  )) %>% 
  mutate(covid_status = factor(covid_status, 
                               levels = c("Negative", "Symptomatic (not confirmed)",
                                          "Asymptomatic confirmed", "Symptomatic confirmed"))) %>% 
  left_join(select(reference_homes, home_code, country, region_UK,
                   staff_to_bed_ratio, carer_to_bed_ratio, bed_tot_category)) %>% 
  left_join(distinct(select(incidents, resident_id, starts_with("covid_first"))))

# CARE HOME AGGREGATES
home_total_confirmed_DAT <- filter(incidents, !is.na(covid_first_symptomatic)) %>% 
  group_by(home_code) %>% 
  summarise(DAT_confirmed = tidyr::replace_na(n_distinct(resident_id), 0))
home_total_confirmed_CT <- new_cases %>% group_by(home_code) %>% 
  summarise(CT_confirmed = sum(tidyr::replace_na(new_confirmed_home, 0) + 
                                 tidyr::replace_na(new_confirmed_hospital, 0)))

@@

residents_ct <- tibble(date = seq(date_min, date_max_tallies, 1)) %>% 
  left_join(distinct(new_cases, date, home_code, 
                     new_confirmed_home, new_confirmed_hospital)) %>% 
  filter(!is.na(home_code)) %>% 
  left_join(distinct(reference_homes, home_code, home_name_datix, postcode, staff_total, nursing_dementia, nursing_general, residential_dementia, residential_general, younger_person)) %>% 
  left_join(select(reference_geography, postcode, region_UK)) %>% 
  left_join(approx_occupancy) %>% 
  arrange(date)

km_ct_residents_confirmed <- residents_ct %>% 
  group_by(date, region_UK) %>% 
  summarise(
    confirmed = sum(tidyr::replace_na(new_confirmed_home, 0) + 
                      tidyr::replace_na(new_confirmed_hospital, 0)),
    occupancy = sum(tidyr::replace_na(susceptible_confirmed, 0))
  ) %>% 
  group_by(region_UK) %>% 
  km_ct_estimator(df = ., t = date, d = confirmed, 
                  pop = occupancy, subtract_cases = FALSE, overwrite = TRUE) %>% 
  ungroup() %>% 
  mutate(
    St_max = S_t^exp(1.96*S_t_SElog),
    St_min = S_t^exp(-1.96*S_t_SElog)
  )

residents_ct_symp <- tibble(date = seq(date_min, date_max_tallies, 1)) %>% 
  left_join(distinct(new_cases, date, home_code, 
                     new_symptomatic_home, new_symptomatic_hospital)) %>% 
  filter(!is.na(home_code)) %>% 
  left_join(distinct(reference_homes, home_code, home_name_datix, postcode)) %>% 
  left_join(select(reference_geography, postcode, region_UK)) %>% 
  left_join(approx_occupancy) %>% 
  arrange(date)

km_ct_residents_symp <- residents_ct_symp %>% 
  group_by(date, region_UK) %>% 
  summarise(
    symptomatic = sum(tidyr::replace_na(new_symptomatic_home, 0) + 
                      tidyr::replace_na(new_symptomatic_hospital, 0)),
    occupancy = sum(tidyr::replace_na(susceptible_symptomatic, 0))
  ) %>% 
  group_by(region_UK) %>% 
  km_ct_estimator(df = ., t = date, d = symptomatic, 
                  pop = occupancy, subtract_cases = FALSE, overwrite = TRUE) %>% 
  ungroup() %>% 
  mutate(
    St_max = S_t^exp(1.96*S_t_SElog),
    St_min = S_t^exp(-1.96*S_t_SElog)
  )

staff_ct <- tibble(date = seq(date_min, date_max_tallies, 1)) %>% 
  left_join(distinct(new_cases, date, home_code, 
                     new_colleague_confirmed, new_colleague_symptomatic)) %>% 
  filter(!is.na(home_code)) %>% 
  left_join(distinct(reference_homes, home_code, home_name_datix, postcode, staff_total, nursing_dementia, nursing_general, residential_dementia, residential_general, younger_person)) %>% 
  left_join(select(reference_geography, postcode, region_UK)) %>% 
  arrange(date)

km_staff_symptomatic <- staff_ct %>% 
  group_by(date, region_UK) %>% 
  summarise(
    confirmed = sum(tidyr::replace_na(new_colleague_confirmed, 0)),
    symptomatic = sum(tidyr::replace_na(new_colleague_symptomatic, 0)),
    staff_total = sum(staff_total)
  ) %>% 
  group_by(region_UK) %>% 
  km_ct_estimator(., t=date, d=symptomatic, pop=staff_total,subtract_cases = TRUE) %>% 
  ungroup() %>% 
  mutate(
    St_max = S_t^exp(1.96*S_t_SElog),
    St_min = S_t^exp(-1.96*S_t_SElog)
  )

km_staff_confirmed <- staff_ct %>% 
  group_by(date, region_UK) %>% 
  summarise(
    confirmed = sum(tidyr::replace_na(new_colleague_confirmed, 0)),
    symptomatic = sum(tidyr::replace_na(new_colleague_symptomatic, 0)),
    staff_total = sum(staff_total)
  ) %>% 
  group_by(region_UK) %>% 
  km_ct_estimator(., date, confirmed, staff_total) %>% 
  ungroup() %>% 
  mutate(
    St_max = S_t^exp(1.96*S_t_SElog),
    St_min = S_t^exp(-1.96*S_t_SElog)
  )

@@

```{r descriptives}
desc_residents <- list()
desc_residents$total_residents <- dplyr::n_distinct(residents_overview$resident_id)

#COUNTS
desc_residents$CT_total_symptomatic <- sum(new_cases$new_symptomatic_home, na.rm=T) + 
  sum(new_cases$new_symptomatic_hospital, na.rm=T)
desc_residents$CT_total_symptomatic_denom <- sum(km_ct_residents_symp$n_t)
desc_residents[paste0(
  "CT_p_symptomatic", c("", "_lower", "_upper")
)] <- epitools::binom.exact(desc_residents$CT_total_symptomatic,
                            desc_residents$total_residents)[
                              c("proportion", "lower", "upper")
                            ] * 100

@@

desc_residents[paste0(
  "CT_p_confirmed", c("", "_lower", "_upper")
)] <- epitools::binom.exact(desc_residents$CT_total_confirmed,
                            desc_residents$total_residents)[
                              c("proportion", "lower", "upper")
                            ] * 100

@@

desc_residents$DAT_total_symptomatic <- n_distinct(filter(incidents, !is.na(covid_first_symptomatic))$resident_id)
desc_residents$DAT_total_symptomatic_denom <- sum(residents_overview$susceptible_symptomatic_days)
desc_residents[paste0(
  "DAT_p_symptomatic", c("", "_lower", "_upper")
)] <- epitools::binom.exact(desc_residents$DAT_total_symptomatic,
                            desc_residents$total_residents)[
                              c("proportion", "lower", "upper")
                            ] * 100
desc_residents[paste0(
  "DAT_IR_symptomatic", c("", "_lower", "_upper")
)] <- epitools::pois.exact(desc_residents$DAT_total_symptomatic,
                            desc_residents$DAT_total_symptomatic_denom)[
                              c("rate", "lower", "upper")
                            ] * 100000

@@

desc_residents$DAT_total_confirmed_denom <- sum(residents_overview$susceptible_confirmed_days)
desc_residents[paste0(
  "DAT_p_confirmed", c("", "_lower", "_upper")
)] <- epitools::binom.exact(desc_residents$unique_residents_test_result_positive,
                            desc_residents$total_residents)[
                              c("proportion", "lower", "upper")
                            ] * 100

@@

desc_residents$DAT_total_deaths <- sum(residents_overview$status == "Deceased")
desc_residents$total_denom <- sum(residents_overview$resident_days)
desc_residents[paste0(
  "DAT_p_death",  c("", "_lower", "_upper")
)] <- epitools::binom.exact(
  desc_residents$DAT_total_deaths,
  desc_residents$total_residents
)[c("proportion", "lower", "upper")] *100

@@

### Homes
desc_residents$total_homes <- n_distinct(home_total_confirmed$home_code)
desc_residents$CT_zero_case <- sum(home_total_confirmed$CT_confirmed == 0)
desc_residents$DAT_zero_case <- sum(home_total_confirmed$DAT_confirmed == 0)
```

```{r captions}
## TABLES
table_nums <- captioner::captioner(prefix = "Table")
tab_national_descriptives <- table_nums(
  name = "tab_national_descriptives",
  caption = "Total homes, beds, and residents within FSHCG and nationwide")
tab_resident_descriptives <- table_nums(
  name = "tab_resident_descriptives",
  caption = paste0("Breakdown of FSHCG residents by care home type, sex, age, region and status on study exit (", format(date_min, "%d/%m/%y"), "-", format(date_max, "%d/%m/%y"), ")"))
tab_zero_cases <- table_nums(
  name = "tab_zero_cases",
  caption = "Number and proportion of homes without confirmed cases by UK region"
)
tab_CoxPH_confirmed <- table_nums(
  name = "tab_CoxPH_confirmed",
  caption =  paste0("Factors associated with the hazard of become a confirmed case: hazard ratios (HR) from a Cox proportional hazards model (n=", 
  formatbm(dplyr::n_distinct(residents_overview$resident_id)),
  ")"))
tab_CoxPH_death <- table_nums(
  name = "tab_CoxPH_death",
  caption =  paste0("Factors associated with all-cause mortality: hazard ratios (HR) from a Cox proportional hazards model (n=", 
  formatbm(dplyr::n_distinct(residents_overview$resident_id)),
  ")"))

supp_epi_CT <- table_nums(
  name = "supp_epi_CT",
  caption =  paste0("Incidence proportions and rates of SARS-CoV-2 infections in residents and staff according to FSHCG manager counts (", format(date_min, "%d/%m/%y"), "-", format(date_max, "%d/%m/%y"), ")"))
supp_epi_DAT <- table_nums(
  name = "supp_epi_DAT",
  caption =  paste0("Incidence proportions and rates of SARS-CoV-2 infections amongst residents according to Datix incident reports (", format(date_min, "%d/%m/%y"), "-", format(date_max, "%d/%m/%y"), ")"))

@@

england_results <- list()
england_results$n_positive = sum(inner_join(new_cases, filter(reference_homes, country == "England"))[c("new_confirmed_home", "new_confirmed_hospital")], na.rm = T)
england_results$n_negative = n_distinct(inner_join(residents, filter(reference_homes, country == "England"))$resident_id) - england_results$n_positive

@@

## Individual-level residents data

>>>>

---
title: "Incidence of confirmed COVID-19 cases in care home staff and residents: Cohort study using electronic records in a large UK care home provider (March-June 2020)"
# author: "Dutey-Magni, PF, Williams, H, Hayward, A, Shallcross, L"
bibliography: references.bib
csl: elsevier-vancouver.csl
output:
  html_document:
    df_print: paged
    toc: yes
    code_folding: hide
  word_document:
    toc: yes
    reference_docx: template.docx
link-citations: yes
always_allow_html: yes
---

@@

date_min <- as.Date("2020-03-02")
date_max <- as.Date("2020-06-07") #as.Date("2020-06-15")
date_min_tallies = as.Date("2020-03-24")
date_max_tallies = as.Date("2020-06-07")

@@

reference_homes <- reference_homes %>% 
  filter(home_code %in% home_inclusion) %>% 
  left_join(select(filter(beds, year=="2020"), -year)) %>% 
  mutate(staff_to_bed_ratio = staff_total/beds,
         carer_to_bed_ratio = (staff_care_assistants + staff_nurses)/beds,
         bed_tot_category = cut(.$beds, 
           breaks = seq(20,100,25), right = F, 
           paste0(seq(20, 80, 25), "–", seq(34, 94, 25), " beds"))
         )

@@

occupancy_interpolated <- resident_days_linear_approx() %>% 
  # TODO: currently putting the individual-level occup for 360 because no occ tally is known!
  # it's got 57 bed including 5 contract beds, so 
  left_join(transmute(filter(approx_occupancy, home_code == "360"), 
                      date, home_code  , occup360 = trunc(occupancy * 57/52)),
            by = c("home_code", "date")) %>%
  mutate(occupancy = if_else(home_code == "360", occup360, occupancy)) %>% 
  select(-occup360)

home_mean_occupancy <- occupancy_interpolated  %>% 
  filter(between(date, date_min_tallies, date_max_tallies)) %>% 
  group_by(home_code) %>% 
  summarise(mean_occupancy = mean(occupancy, na.rm = T))

reference_homes <- reference_homes %>% 
  left_join(home_mean_occupancy) %>% 
  mutate(pct_occupancy = mean_occupancy/beds)

residents_episodes <- tline %>% 
  filter(rday==1) %>% 
  group_by(resident_id, home_code, dob, gender, 
           status, home_type, user_type2,
           susceptible_symptomatic, 
           susceptible_confirmed) %>% 
  summarise(entry_date = min(date),
            exit_date = max(date+1),
            resident_days = sum(rday),
            susceptible_symptomatic_days = sum(susceptible_symptomatic),
            susceptible_confirmed_days = sum(susceptible_confirmed)) %>% 
  mutate(date1 = as.numeric( entry_date - date_min),
         date2 = as.numeric(exit_date - date_min),
         ageg = cut_age_denary(compute_age(dob, date_min), age.min = 75, age.max = 95)) %>% 
  mutate(symptomatic = -susceptible_symptomatic+1,
         confirmed = -susceptible_confirmed+1,
         symptomatic_confirmed = (-susceptible_symptomatic+1)*(-susceptible_confirmed+1),
         date2 = if_else(date1 == date2, date2 + 1, date2)) %>% 
  mutate(covid_status = case_when(
    symptomatic==0 & confirmed == 0 ~ "Negative",
    symptomatic==1 & confirmed == 0 ~ "Symptomatic (not confirmed)",
    symptomatic==0 & confirmed == 1 ~ "Asymptomatic confirmed",
    symptomatic==1 & confirmed == 1 ~ "Symptomatic confirmed"
  )) %>% 
  mutate(covid_status = factor(covid_status, 
                               levels = c("Negative", "Symptomatic (not confirmed)",
                                          "Asymptomatic confirmed", "Symptomatic confirmed")),
         ageg = cut_age_denary(compute_age(dob, date_min), age.min = 75, age.max = 95))   %>% 
  left_join(select(reference_homes, home_code, country, region_UK,
                   staff_to_bed_ratio, carer_to_bed_ratio, bed_tot_category, beds, pct_occupancy)) %>% 
  group_by(resident_id) %>% 
  mutate(death_status = if_else(
    date1 == max(date1),
    as.integer(status == "Deceased"),
    0L
  )) %>% 
  ungroup()

residents_overview <- tline %>% 
  filter(rday==1) %>%
  mutate(ageg = cut_age_denary(compute_age(dob, date_min), age.min = 75, age.max = 95)) %>% 
  group_by(resident_id, home_code, ageg, gender, 
           admission_type2, home_type, user_type2, status) %>% 
  summarise(resident_days = sum(rday),
            susceptible_symptomatic_days = sum(susceptible_symptomatic),
            susceptible_confirmed_days = sum(susceptible_confirmed),
            symptomatic = max(-susceptible_symptomatic+1, na.rm = T),
            confirmed = max(-susceptible_confirmed+1, na.rm = T),
            start_date = min(date, na.rm = T),
            stop_date = max(date, na.rm = T),
            start_int = as.numeric(min(date, na.rm = T) - date_min),
            stop_int = as.numeric(max(date, na.rm = T)- date_min)
    ) %>% 
  ungroup() %>% 
  mutate(covid_status = case_when(
    symptomatic==0 & confirmed == 0 ~ "Negative",
    symptomatic==1 & confirmed == 0 ~ "Symptomatic (not confirmed)",
    symptomatic==0 & confirmed == 1 ~ "Asymptomatic confirmed",
    symptomatic==1 & confirmed == 1 ~ "Symptomatic confirmed"
  )) %>% 
  mutate(covid_status = factor(covid_status, 
                               levels = c("Negative", "Symptomatic (not confirmed)",
                                          "Asymptomatic confirmed", "Symptomatic confirmed"))) %>% 
  left_join(select(reference_homes, home_code, country, region_UK,
                   staff_to_bed_ratio, carer_to_bed_ratio, bed_tot_category, beds, beds, pct_occupancy)) %>% 
  left_join(distinct(select(incidents, resident_id, starts_with("covid_first"))))

# CARE HOME AGGREGATES
home_total_confirmed_DAT <- filter(residents_overview, !is.na(covid_first_confirmed)) %>% 
  filter(between(covid_first_confirmed, date_min_tallies, date_max_tallies)) %>% 
  group_by(home_code) %>% 
  summarise(DAT_confirmed = tidyr::replace_na(n_distinct(resident_id), 0))
home_total_confirmed_CT <- new_cases %>% group_by(home_code) %>% 
  summarise(CT_confirmed = sum(tidyr::replace_na(new_confirmed_home, 0) + 
                                 tidyr::replace_na(new_confirmed_hospital, 0)))

@@

residents_ct <- tibble(date = seq(date_min, date_max_tallies, 1)) %>% 
  left_join(distinct(new_cases, date, home_code, 
                     new_confirmed_home, new_confirmed_hospital,
                     new_symptomatic_home, new_symptomatic_hospital)) %>% 
  filter(!is.na(home_code)) %>% 
  left_join(distinct(reference_homes, home_code, home_name_datix, postcode, staff_total, nursing_dementia, nursing_general, residential_dementia, residential_general, younger_person)) %>% 
  left_join(select(reference_geography, postcode, region_UK)) %>% 
  left_join(occupancy_interpolated) %>% 
  arrange(home_code, date) %>% 
  group_by(home_code) %>% 
  mutate(new_symptomatic = tidyr::replace_na(new_symptomatic_home, 0) +
                                    tidyr::replace_na(new_symptomatic_hospital, 0),
         new_confirmed = tidyr::replace_na(new_confirmed_home, 0) +
                                    tidyr::replace_na(new_confirmed_hospital, 0)) %>% 
  mutate(I_symptomatic = total_cases_in_home(occupancy, new_symptomatic, date),
         I_confirmed = total_cases_in_home(occupancy, new_confirmed, date)) %>% 
  ungroup()

km_ct_residents_confirmed <- residents_ct %>% 
  group_by(date, region_UK) %>% 
  summarise(
    confirmed = sum(new_confirmed),
    I_confirmed = round(sum(I_confirmed)),
    occupancy = sum(occupancy)
  ) %>% 
  group_by(region_UK) %>% 
  km_ct_estimator(df = ., t = date, d = confirmed, 
                  pop = (occupancy - I_confirmed), subtract_cases = FALSE, overwrite = TRUE) %>% 
  ungroup() %>% 
  mutate(
    St_max = S_t^exp(1.96*S_t_SElog),
    St_min = S_t^exp(-1.96*S_t_SElog)
  )

# residents_ct_symp <- tibble(date = seq(date_min, date_max_tallies, 1)) %>% 
#   left_join(distinct(new_cases, date, home_code, 
#                      new_symptomatic_home, new_symptomatic_hospital)) %>% 
#   filter(!is.na(home_code)) %>% 
#   left_join(distinct(reference_homes, home_code, home_name_datix, postcode)) %>% 
#   left_join(select(reference_geography, postcode, region_UK)) %>% 
#   left_join(occupancy_interpolated) %>% 
#   arrange(date)

km_ct_residents_symp <- residents_ct %>% 
  group_by(date, region_UK) %>% 
  summarise(
    symptomatic = sum(new_symptomatic),
    I_symptomatic = round(sum(I_symptomatic)),
    occupancy = sum(occupancy)
  ) %>% 
  group_by(region_UK) %>% 
  km_ct_estimator(df = ., t = date, d = symptomatic, 
                  pop = (occupancy - I_symptomatic), subtract_cases = FALSE, overwrite = TRUE) %>% 
  ungroup() %>% 
  mutate(
    St_max = S_t^exp(1.96*S_t_SElog),
    St_min = S_t^exp(-1.96*S_t_SElog)
  )

staff_ct <- tibble(date = seq(date_min, date_max_tallies, 1)) %>% 
  left_join(distinct(new_cases, date, home_code, 
                     new_colleague_confirmed, new_colleague_symptomatic)) %>% 
  filter(!is.na(home_code)) %>% 
  left_join(distinct(reference_homes, home_code, home_name_datix, postcode, staff_total, nursing_dementia, nursing_general, residential_dementia, residential_general, younger_person)) %>% 
  left_join(select(reference_geography, postcode, region_UK))  %>% 
  arrange(date) %>% 
  group_by(home_code) %>% 
  mutate(
    new_colleague_confirmed = tidyr::replace_na(new_colleague_confirmed, 0),
    new_colleague_symptomatic = tidyr::replace_na(new_colleague_symptomatic, 0)
    ) %>% 
  mutate(I_symptomatic = total_cases_in_home(staff_total, new_colleague_symptomatic, date),
         I_confirmed = total_cases_in_home(staff_total, new_colleague_confirmed, date)) %>% 
  ungroup()

km_staff_symptomatic <- staff_ct %>% 
  group_by(date, region_UK) %>% 
  summarise(
    symptomatic = sum(new_colleague_symptomatic),
    I_symptomatic = round(sum(I_symptomatic)),
    staff_total = sum(staff_total)
  ) %>% 
  group_by(region_UK) %>% 
  km_ct_estimator(., t=date, d=symptomatic, pop=(staff_total-I_symptomatic),
                  subtract_cases = FALSE, overwrite = TRUE) %>% 
  ungroup() %>% 
  mutate(
    St_max = S_t^exp(1.96*S_t_SElog),
    St_min = S_t^exp(-1.96*S_t_SElog)
  )

km_staff_confirmed <- staff_ct %>% 
  group_by(date, region_UK) %>% 
  summarise(
    confirmed = sum(new_colleague_confirmed),
    I_confirmed = round(sum(I_confirmed)),
    staff_total = sum(staff_total)
  ) %>% 
  group_by(region_UK) %>% 
  km_ct_estimator(., t=date, d=confirmed, pop=(staff_total-I_confirmed),
                  subtract_cases = FALSE, overwrite = TRUE) %>% 
  ungroup() %>% 
  mutate(
    St_max = S_t^exp(1.96*S_t_SElog),
    St_min = S_t^exp(-1.96*S_t_SElog)
  )

@@

```{r descriptives}
desc_residents <- list()
desc_residents$DAT_total_residents <- dplyr::n_distinct(residents_overview$resident_id)
desc_residents$DAT_total_residents_england <- dplyr::filter(residents_overview, country == "England") %>% summarise(n = dplyr::n_distinct(resident_id)) %>% .$n

#COUNTS
# This is estimated in validation.Rmd
desc_residents$CT_total_residents <- round(desc_residents$DAT_total_residents * 1.117309 + .49)
desc_residents$CT_total_residents_england <- round(desc_residents$DAT_total_residents_england * 1.0793268 + .49)
desc_residents$CT_total_symptomatic <- sum(new_cases$new_symptomatic_home, na.rm=T) + 
  sum(new_cases$new_symptomatic_hospital, na.rm=T)
desc_residents$CT_total_symptomatic_denom <- sum(km_ct_residents_symp$n_t)
desc_residents[paste0(
  "CT_p_symptomatic", c("", "_lower", "_upper")
)] <- epitools::binom.exact(desc_residents$CT_total_symptomatic,
                            desc_residents$CT_total_residents)[
                              c("proportion", "lower", "upper")
                            ] * 100

@@

desc_residents[paste0(
  "CT_p_confirmed", c("", "_lower", "_upper")
)] <- epitools::binom.exact(desc_residents$CT_total_confirmed,
                            desc_residents$CT_total_residents)[
                              c("proportion", "lower", "upper")
                            ] * 100

@@

desc_residents$DAT_total_symptomatic <- n_distinct(filter(incidents, !is.na(covid_first_symptomatic))$resident_id)
desc_residents$DAT_total_symptomatic_denom <- sum(residents_overview$susceptible_symptomatic_days)
desc_residents[paste0(
  "DAT_p_symptomatic", c("", "_lower", "_upper")
)] <- epitools::binom.exact(desc_residents$DAT_total_symptomatic,
                            desc_residents$DAT_total_residents)[
                              c("proportion", "lower", "upper")
                            ] * 100
desc_residents[paste0(
  "DAT_IR_symptomatic", c("", "_lower", "_upper")
)] <- epitools::pois.exact(desc_residents$DAT_total_symptomatic,
                            desc_residents$DAT_total_symptomatic_denom)[
                              c("rate", "lower", "upper")
                            ] * 100000

@@

desc_residents$DAT_total_confirmed_denom <- sum(residents_overview$susceptible_confirmed_days)
desc_residents[paste0(
  "DAT_p_confirmed", c("", "_lower", "_upper")
)] <- epitools::binom.exact(desc_residents$unique_residents_test_result_positive,
                            desc_residents$DAT_total_residents)[
                              c("proportion", "lower", "upper")
                            ] * 100

@@

desc_residents$DAT_total_deaths <- sum(residents_overview$status == "Deceased")
desc_residents$total_denom <- sum(residents_overview$resident_days)
desc_residents[paste0(
  "DAT_p_death",  c("", "_lower", "_upper")
)] <- epitools::binom.exact(
  desc_residents$DAT_total_deaths,
  desc_residents$DAT_total_residents
)[c("proportion", "lower", "upper")] *100

@@

### Homes
desc_residents$total_homes <- n_distinct(home_total_confirmed$home_code)
desc_residents$CT_zero_case <- sum(home_total_confirmed$CT_confirmed == 0)
desc_residents$DAT_zero_case <- sum(home_total_confirmed$DAT_confirmed == 0)

## OUTBREAK HOMES 
desc_residents_outbreak_only <- list()
desc_residents_outbreak_only$outbreak_homes <- home_total_confirmed$home_code[home_total_confirmed$CT_confirmed != 0]

desc_residents_outbreak_only$CT_total_beds <- beds %>% 
  filter(year == 2020 & home_code %in% desc_residents_outbreak_only$outbreak_homes) %>% 
  summarise(beds = sum(beds),
            contract_beds = sum(contract_beds))

desc_residents_outbreak_only$CT_total_residents <- residents_overview %>% 
  dplyr::filter(home_code %in% desc_residents_outbreak_only$outbreak_homes) %>% 
  dplyr::summarise(total_residents = round(dplyr::n_distinct(resident_id)* 1.1151324 + .49)) %>% 
  .$total_residents

desc_residents_outbreak_only$CT_total_confirmed <- new_cases %>% 
  filter(home_code %in% desc_residents_outbreak_only$outbreak_homes) %>% 
  summarise(n = sum(new_confirmed_home, na.rm = T) + sum(new_confirmed_hospital, na.rm = T)) %>% 
  .$n

desc_residents_outbreak_only$CT_total_symptomatic <- new_cases %>% 
  filter(home_code %in% desc_residents_outbreak_only$outbreak_homes) %>% 
  summarise(n = sum(new_symptomatic_home, na.rm = T) + sum(new_symptomatic_hospital, na.rm = T)) %>% 
  .$n

desc_residents_outbreak_only$CT_total_confirmed_denom <- residents_ct %>% 
  filter(home_code %in% desc_residents_outbreak_only$outbreak_homes) %>% 
  summarise(n = sum(occupancy - I_confirmed)) %>% 
  .$n

desc_residents_outbreak_only[paste0(
  "CT_p_confirmed", c("", "_lower", "_upper")
)] <- epitools::binom.exact(desc_residents_outbreak_only$CT_total_confirmed,
                            desc_residents_outbreak_only$CT_total_residents)[
                              c("proportion", "lower", "upper")
                              ] * 100

desc_residents_outbreak_only[paste0(
  "CT_IR_confirmed", c("", "_lower", "_upper")
)] <- epitools::pois.exact(desc_residents_outbreak_only$CT_total_confirmed,
                           desc_residents_outbreak_only$CT_total_confirmed_denom)[
                             c("rate", "lower", "upper")
                             ] * 100000

desc_residents_outbreak_only$CT_total_symptomatic <-  new_cases %>% 
  filter(home_code %in% desc_residents_outbreak_only$outbreak_homes) %>% 
  summarise(n = sum(new_symptomatic_home, na.rm = T) + sum(new_symptomatic_hospital, na.rm = T)) %>% 
  .$n

desc_residents_outbreak_only$CT_total_symptomatic_denom <- residents_ct %>% 
  filter(home_code %in% desc_residents_outbreak_only$outbreak_homes) %>% 
  summarise(n = sum(occupancy - I_symptomatic)) %>% 
  .$n

desc_residents_outbreak_only[paste0(
  "CT_p_symptomatic", c("", "_lower", "_upper")
)] <- epitools::binom.exact(desc_residents_outbreak_only$CT_total_symptomatic,
                            desc_residents_outbreak_only$CT_total_residents)[
                              c("proportion", "lower", "upper")
                            ] * 100
desc_residents_outbreak_only[paste0(
  "CT_IR_symptomatic", c("", "_lower", "_upper")
)] <- epitools::pois.exact(desc_residents_outbreak_only$CT_total_symptomatic,
                            desc_residents_outbreak_only$CT_total_symptomatic_denom)[
                              c("rate", "lower", "upper")
                            ] * 100000

```{r captions}
## TABLES
table_nums <- captioner::captioner(prefix = "Table")
tab_national_descriptives <- table_nums(
  name = "tab_national_descriptives",
  caption = "Total homes, beds, contract beds, and residents within FSHCG and nationwide")
tab_resident_descriptives <- table_nums(
  name = "tab_resident_descriptives",
  caption = paste0("Breakdown of FSHCG private bed residents by care home type, sex, age, region and status on study exit (", format(date_min, "%d/%m/%y"), "-", format(date_max, "%d/%m/%y"), ")"))
supp_epi_CT <- table_nums(
  name = "supp_epi_CT",
  caption =  paste0("Incidence proportions and rates of SARS-CoV-2 infections in residents and staff according to FSHCG manager counts (", format(date_min, "%d/%m/%y"), "-", format(date_max, "%d/%m/%y"), ")"))
supp_epi_CT_oubreak_only <- table_nums(
  name = "supp_epi_CT_oubreak_only",
  caption =  paste0("Incidence proportions and rates of SARS-CoV-2 infections among residents of outbreak care homes according to FSHCG manager counts (", format(date_min, "%d/%m/%y"), "-", format(date_max, "%d/%m/%y"), ")"))
tab_CoxPH_confirmed <- table_nums(
  name = "tab_CoxPH_confirmed",
  caption =  paste0("Factors associated with the hazard of become a confirmed case: hazard ratios (HR) from a Cox proportional hazards model (n=", 
  formatbm(dplyr::n_distinct(residents_overview$resident_id)),
  ")"))
tab_CoxPH_death <- table_nums(
  name = "tab_CoxPH_death",
  caption =  paste0("Factors associated with all-cause mortality: hazard ratios (HR) from a Cox proportional hazards model (n=", 
  formatbm(dplyr::n_distinct(residents_overview$resident_id)),
  ")"))

supp_epi_DAT <- table_nums(
  name = "supp_epi_DAT",
  caption =  paste0("Incidence proportions and rates of SARS-CoV-2 infections amongst residents according to Datix incident reports (", format(date_min, "%d/%m/%y"), "-", format(date_max, "%d/%m/%y"), ")"))

tab_zero_cases <- table_nums(
  name = "tab_zero_cases",
  caption = paste0("Number and proportion of homes without confirmed cases by UK region (", format(date_min_tallies, "%d/%m/%y"), "-", format(date_max_tallies, "%d/%m/%y"), ")")
)

@@

england_results <- list()
england_results$n_positive = sum(inner_join(new_cases, filter(reference_homes, country == "England"))[c("new_confirmed_home", "new_confirmed_hospital")], na.rm = T)
england_results$n_negative = desc_residents$CT_total_residents_england  - england_results$n_positive

@@

## Aggregate outbreak data (`r format(date_min_tallies, "%d/%m/%Y")`--`r format(date_max_tallies, "%d/%m/%Y")` )
